\gdef\problemNumber{GT A-7.4}
\def\problemText{
The game of \emph{Hex} is said to have, as one of its inventors, the
mathematician John Nash, who is the subject of the book and movie \emph{A
Beautiful Mind}. In this game, two players, one playing black and the other
playing white, take turns placing stones of their respective colors on an
$n\,\times\,n$ hexagonal grid. Once a stone is placed, it cannot be moved. The
black player's goal is to connect the top and bottom sides of the grid, and the
white player's goal is to connect the left and right sides of the grid, using
stones of their respective colors. Two cells are considered connected if they
share an edge and both have the same color stone. (See Figure~$7.12$.) Describe
an efficient scheme where you can determine after each move whether black or
white has just won a game of Hex.\\[12pt]
}
\def\problemSolution{
\textcolor{blue}{
\textbf{Answer:}\\[6pt]
We will have four nodes for: Top, Bottom, Left and Right sides. \\[6pt]
A node for each cell in the grid. \\[6pt]
Black Player's goal: Connect Top and Bottom\\[6pt]
White Player's goal: Connect Left and Right\\[6pt]
\\[6pt]
If the black stone is placed on Top or Bottom nodes we do:\\[6pt]
    Union(stone, Top) or Union(stone, Bottom)\\[6pt]
    Plus check if the neighbor has black stone.\\[6pt]
    If so, we do the Union with the neighbor. \\[6pt]
If black stone is placed anywhere else, we check if it has black neighbor. \\[6pt]
If so we do Union with neighbor.\\[6pt]
\\[6pt]
We do same steps for the White. \\[6pt]
\\[6pt]
To find the winner:\\[6pt]
We check if Top and Bottom are in same set everytime black stone is placed. Find(Top) = Find(Bottom). \\[6pt]
If so Black wins. This means top and bottom are connected with same color stones\\[6pt]
We check if Left and Right are in same set everytime white stone is placed. Find(Left) = Find(Right).\\[6pt]
If so White wins. This means left and right are connected with same color stones.\\[6pt]
}
}
\gdef\problemOutcomes{CS 6, 5870-1}
